Secure Multi-Party Computation with SCALE-MAMBA

### 2019-04-22 paper.tex
Car commit: nearly finished finally

GENERATION OF BEAVER TRIPLES: Include protocol on how triples are distributively generated without revealing them
BGV emcryption scheme

For the generation of a beaver triple $(a,b,c)$ , the Brakerski-Gentry-Vaikuntanathan encryption scheme~\cite{cryptoeprint:2011:277} is used, which has homomorphic properties for addition and multiplication. It is a public key crypto system, where the parties can only decrypt an encryption together. Be $Enc_{pk}$ the encryption with the public key, and $Dec$ the distributed decryption. The triples are generated as follows:

\begin{itemize}
\item Every party $P_i$ samples a random $a_i$ and $b_i$, so that $a=a_1+...+a_n$ and $b=b_1+...+b_n$
\item Every party computes $e_{a_i}=Enc_{pk}(a_i)$ and $e_{b__i}=Enc_{pk}()$ and broadcasts the values
\item Every party computes $e_a=e_{a_1}+...+$

Generation described in Overdrive
sample ai,bi
every pair ij:
i->j enc(ai)
pj: cij= bj*enc(a_i)-enc'(random e)
ci=ao*bi+

Given public key encryption, where the parties can decrypt together the result

random a,b shared
enc ai, encbi, broadcast
compute enca, encb

random fi so that f=fi
compute encf +encm
dec f+m
m1=m+f-f, mi=-fi

>>>>

For the generation of a beaver triple $(a,b,c)$, homomorphic public key cryptography based on the Brakerski-Gentry-Vaikuntanathan encryption scheme~\cite{cryptoeprint:2011:277} is used. Every party $P_i$ generates for the communication with each party $P_j$ a set of keys $(pk_{ij},sk_{ij})$. Then, one triple is generated as follows:

\begin{enumerate}
\item Every party $P_i$ samples a random $a_i$ and $b_i$; then $a=\sum_{j=1}^n a_i$ and $b=\sum_{j=1}^n b_i$
\item Every party $P_i$ executes following protocol with each other party $P_j$:
\begin{enumerate}
\item $P_i$ sends $P_j$ $Enc_{pk_{ij}}(a_i)$
\item $P_j$ samples random $e_{ij}$, calculates $g_{ij}=b_j*Enc_{pk_{ij}}(a_i)-Enc_{pk_{ij}}(e_{ij})$ and sends $g_{ij}$ it to $P_i$
\item $P_i$ decrypts $d_{ij}=Dec_{sk_{ij}}(g_{ij})$
\end{enumerate}
\item Every party $P_i$ computes $c_i=a_i*b_i+\sum_{i \neq j} (e_{ij}+d_{ij})$
\end{enumerate}
Now, $c$ is correctly shared so that $c=c_1+...+c_n$.\\
\textbf{Correctness:}
$$d_{ij}=b_j*a_i-e_{ij}$$
$$c_i=a_i*b_i+\sum_{i \neq j} (e_{ij}+d_{ij})= a_i*b_i+ \sum_{i \neq j} (b_j*a_i)$$
$$c_i= a_i*b_i+ a_i*\sum_{i \neq j} (b_j)=a_i*(b_i+ \sum_{i \neq j} b_j)=a_i*b$$
$$c=c_1+...+c_n=a_1*b+...+a_n*b=(a_1+...+a_n)*b=a*b$$
